Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Further polishing

\begin{theorem}\label{normal form}
If there is a derivation $q : c_1 \Leftrightarrow c_2$, then there exists a
bijective lens $\ell : K(c_1) \Leftrightarrow K(c_2)$ such that:
\begin{align*}
\llbracket q \rrbracket.\get &= \llbracket \ell \rrbracket\circ
\canonizer(c_1)\\
\llbracket q \rrbracket.\lput &= \llbracket \ell \rrbracket^{-1} \circ
\canonizer(c_2)
\end{align*}
\end{theorem}
\begin{proof}
We elide a full proof of this statement, since the proof is attained via a
straightforward induction on the derivation $q_1 : c_1 \Leftrightarrow c_2$ (the
full details can be found in the appendix). Since bijective lenses are closed
under strongly unambiguous regular operators, the tricky case is composition.
The composition case is more involved since we need to show that we can get rid
of the canonizers in the middle:

@@

\end{center}

Consequently,
\begin{align*}
\llbracket q_2 \rrbracket.\get \circ \llbracket q_1 \rrbracket.\get &=
(\llbracket \ell_2 \rrbracket \circ \canonizer(c_3)) \circ (\llbracket \ell_1
\rrbracket \circ \canonizer(c_1))\\
&= \llbracket \ell_2 \rrbracket \circ (\canonizer(c_3) \circ \llbracket \ell_1
\rrbracket) \circ \canonizer(c_1)\\
&= (\llbracket \ell_2 \rrbracket \circ \llbracket \ell_1 \rrbracket) \circ
\canonizer(c_1)\\
&= \llbracket \ell_1 \; ; \; \ell_2 \rrbracket \circ \canonizer(c_1)
\end{align*}
We are permitted to claim the third step from the second since
$\canonizer(c_3)$ is the identity function on $K(c_2)$ which is
syntactically equal to $K(c_3)$ by assumption. A similar argument shows that
$$\llbracket q_1 \rrbracket.\lput \circ \llbracket q_2 \rrbracket.\lput =
\llbracket \ell_1 \; ; \; \ell_2 \rrbracket^{-1} \circ
\canonizer(c_4)$$

The other cases of the proof are similar in that they follow from a
straightforward application of the induction hypothesis followed by unrolling
the equations that give the denotation for QRE lenses.
\end{proof}

>>>>

\begin{theorem}\label{normal form}
If there is a derivation $q : c_1 \Leftrightarrow c_2$, then there exists a
bijective lens $\ell : K(c_1) \Leftrightarrow K(c_2)$ such that:
\begin{align*}
\llbracket q \rrbracket.\get &= \llbracket \ell \rrbracket\circ
\canonizer(c_1)\\
\llbracket q \rrbracket.\lput &= \llbracket \ell \rrbracket^{-1} \circ
\canonizer(c_2)
\end{align*}
\end{theorem}
\begin{proof}
By straightforward induction on the derivation
$q_1 : c_1 \Leftrightarrow c_2$. Since bijective lenses are closed under strongly unambiguous
regular operators, the tricky case is composition.  The composition case is
more involved since we need to show that we can get rid of the canonizers in
the middle:

@@

\end{center}
%
Consequently,
\begin{align*}
\llbracket q_2 \rrbracket.\get \circ \llbracket q_1 \rrbracket.\get &=
(\llbracket \ell_2 \rrbracket \circ \canonizer(c_3)) \circ (\llbracket \ell_1
\rrbracket \circ \canonizer(c_1))\\
&= \llbracket \ell_2 \rrbracket \circ (\canonizer(c_3) \circ \llbracket \ell_1
\rrbracket) \circ \canonizer(c_1)\\
&= (\llbracket \ell_2 \rrbracket \circ \llbracket \ell_1 \rrbracket) \circ
\canonizer(c_1)\\
&= \llbracket \ell_1 \; ; \; \ell_2 \rrbracket \circ \canonizer(c_1)
\end{align*}
We are permitted to claim the third step from the second since
$\canonizer(c_3)$ is the identity function on $K(c_2)$ which is
syntactically equal to $K(c_3)$ by assumption. A similar argument shows that
$$\llbracket q_1 \rrbracket.\lput \circ \llbracket q_2 \rrbracket.\lput =
\llbracket \ell_1 \; ; \; \ell_2 \rrbracket^{-1} \circ
\canonizer(c_4)$$

The other cases of the proof are similar, proceeding by a
straightforward application of the induction hypothesis followed by unrolling
the equations that give the denotation for QRE lenses.  Full details can be
found in the appendix.
\end{proof}
